\textbf{Appendix}\\ Step by Step: Using Integrated Step Selection Analysis to Simulate Wild Dog Dispersal and Assess Landscape Connectivity

### 2021-09-08 Chapter_1/04_Manuscript/Manuscript_2021-08-30.tex
Various updates

%------------------------------------------------------------------------------
%  LONG VERSION
%------------------------------------------------------------------------------
% Importance of dispersal & connectivity and mow its measured
Dispersal of individuals is a crucial prerequisite for long-term species
persistence but depends on a sufficient degree of landscape connectivity. To
date, connectivity has primarily been quantified using least-cost analysis and
circuit theory, albeit both methods make assumptions that are rarely met in
reality. Least-cost analysis assumes that animals move towards a preconceived
destination and choose a cost-minimizing route accordingly, whereas circuit
theory presumes a complete random walk without directional persistence. While
these shortcomings can be overcome by spatio-temporally explicitly simulating
dispersal trajectories from individual-based movement models, a unified
approach for such simulations is lacking.

% What we do
Here, we present a simple three-step workflow to simulate dispersal and asses
landscape connectivity starting from empirical GPS movement data. We exemplify
the workflow using dispersal data collected on the endangered African wild dog
(\textit{Lycaon pictus}) in the Kavango-Zambezi Transfrontier Conservation Area,
the world's largest transboundary conservation area. In step one, we use
integrated step selection functions to parametrize a mechanistic movement model
describing habitat and movement preferences of dispersers. In step two, we
employ the parametrized model to simulate individual dispersal trajectories
across the landscape. In step three, we interpret simulated trajectories by
converting them into three complementary connectivity maps: a heatmap revealing
frequently traversed areas, a betweenness-map delineating dispersal corridors,
and a map of inter-patch connectivity depicting the presence and intensity of
functional links between habitat patches.

% Some results
We find that simulating dispersal from indvidual-based movement models fitted
via step selection functions are readily interpretable and offer great
flexibility to realistically render dispersal movements. Moreover, by not
enforcing connections towards known endpoints but instead letting dispersers
react to the environment as they go, such simulations overcome shortcomings
inherent least-cost path analysis, while at the same time allowing for
autocorrelation in simulated steps, which can not be incorporated using circuit
theory. Inspite of these advantages, simulating dispersal entails numerous
non-trivial modeling decisions, such as the number of simulated individuals and
the duration of simulated dispersal events.

% Case study
We  show that simulations from step-selection functions offer a simple yet
powerful alternative to traditional connectivity modeling techniques, although
necessitating informed decisions about the number of simulated individuals and
the duration of simulated dispersal events. Ultimately, our workflow permits a
more mechanistic understanding of dispersal behaviour and landscape connectivity
making it useful for a variety of applications in ecological, evolutionary, and
conservation research.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width = \textwidth]{99_GraphicalAbstract2.pdf}
    \caption{Flowchart of the simulation-based connectivity analysis as proposed
    in this article. First, GPS data and habitat covariates have to be
    collected. The combined data is then analyzed in an integrated step
    selection model, which enables the parametrization of the focal species'
    habitat and movement kernels and results in a mechanistic movement model.
    The parametrized model is then treated as an individual-based movement model
    and used to simulate dispersal trajectories. Ultimately, simulated
    trajectories serve to produce a set of maps that are pertinent to landscape
    connectivity. This includes a heatmap, indicating the traversal frequency
    across each spatial unit of the study area, a betweenness map, highlighting
    movement corridors and bottlenecks, and, finally, an inter-patch
    connectivity map, where the frequency of connections and their average
    duration can be depicted.}
    \label{GraphicalAbstract}
  \end{center}
\end{figure}

@@

>>>>

%------------------------------------------------------------------------------
%  LONG VERSION
%------------------------------------------------------------------------------
% Importance of Dispersal & Connectivity
Dispersal of individuals is crucial prerequisite for long-term species
persistence. However, the ability to disperse is contingent on a sufficient
degree of landscape connectivity, which is why the identification of movement
corridors that contribute to connectivity has become a task of extraordinary
importance.

% Quantifying connectivity
Over the past two decades, ecologists have investigated connectivity using
graph-based methods, such as least-cost analysis and circuit theory.
Unfortunately, these methods make several assumptions that are rarely met in
reality. Least-cost analysis, for instance, assumes that animals move towards a
preconceived endpoint and choose a cost-minimizing route accordingly. Circuit
theory, in contrast, presumes a random walk without any directional persistence.
To overcome these unrealistic assumptions, dispersal simulations from
individual-based movement models have been proposed and applied, yet a unified
framework to simulate dispersal and assess connectivity is lacking.

% What we do
Here, we combine several already-existing methods to synthesize a simple
three-step workflow for simulating dispersal and assessing connectivity. In step
one, integrated step selection functions are used to parametrize a mechanistic
movement model. In step two, the parametrized model is applied as an
individual-based movement model to simulate dispersal trajectories. In step
three, simulated trajectories are consolidated into three complementary
connectivity maps, each focusing on a different aspect of connectivity. The set
of maps includes a heatmap, revealing frequently traversed areas, a
betweenness-map, delineating dispersal corridors and bottlenecks, and a map of
inter-patch connectivity, depicting the presence or absence of functional links
between habitat patches.

% Case study
We exemplify the application of the proposed workflow to assess landscape
connectivity for dispersing African wild dogs (\textit{Lycaon pictus}) in the
Kavango-Zambezi Transfrontier Conservation Area, the world's largest
transboundary conservation area. We thereby demonstrate that simulations from
integrated step selection functions offer a simple but powerful alternative to
traditional connectivity modeling techniques, although necessitating informed
decisions about the number of simulated individuals and the duration of
simulated dispersal events. After all, the proposed workflow enables to relax
several unrealistic assumptions inherent to graph-based methods and permits a
more mechanistic understanding of landscape connectivity.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width = \textwidth]{99_GraphicalAbstract.pdf}
    \caption{Flowchart of the simulation-based connectivity analysis as proposed
    in this article. First, GPS data and habitat covariates have to be
    collected. The combined data is then analyzed in an integrated step
    selection model, which enables the parametrization of the focal species'
    habitat and movement kernels and results in a mechanistic movement model.
    The parametrized model is then treated as an individual-based movement model
    and used to simulate dispersal trajectories. Ultimately, simulated
    trajectories serve to produce a set of maps that are pertinent to landscape
    connectivity. This includes a heatmap, indicating the traversal frequency
    across each spatial unit of the study area, a betweenness map, highlighting
    movement corridors and bottlenecks, and, finally, an inter-patch
    connectivity map, where the frequency of connections and their average
    duration can be depicted.}
    \label{GraphicalAbstract}
  \end{center}
\end{figure}

@@

\begin{table}
  \begin{center}
  \caption{Most parsimonious movement model for dispersing wild dogs. The
  movement kernel describes preferences of dispersers with regards to movement
  behavior (may also be viewed as movement capability), whereas the habitat
  kernel describes preferences with respect to habitat conditions. Interactions
  between the two kernels indicate that the two kernels are not independent,
  meaning that movement preferences are contingent on habitat conditions. Note
  that all covariates were standardized to a mean of zero and standard deviation
  of 1. Plots to aid with the interpretation of this model are given in Appendix
  S2.}
  \label{MovementModelNumbers}
  \resizebox{\textwidth}{!} {
    \begin{threeparttable}
      \begin{tabular}{llrrrc}
        \toprule
        Kernel & Covariate & Coefficient & SE & p-value & Sign. \\
        \midrule
        \multirow{5}{*}{Habitat Kernel}
         & Water & -0.546 & 0.112 & \(<\) 0.001 & *** \\
         & DistanceToWater \textsuperscript{0.5} & -0.390 & 0.231 & 0.092 & * \\
         & Woodland & -0.364 & 0.086 & \(<\) 0.001 & *** \\
         & Shrubs/Grassland & 0.288 & 0.092 & 0.002 & *** \\
         & HumanInfluence & -0.535 & 0.229 & 0.019 & ** \\
        \hdashline
        \multirow{6}{*}{Movement Kernel}
         & sl & 0.075 & 0.037 & 0.042 & ** \\
         & cos(ta) & 0.105 & 0.031 & 0.001 & *** \\
         & log(sl) & 0.146 & 0.051 & 0.004 & *** \\
         & cos(ta) : sl & 0.049 & 0.026 & 0.064 & * \\
         & cos(ta) : log(sl) & 0.076 & 0.026 & 0.003 & *** \\
         & sl : LowActivity & -0.917 & 0.113 & \(<\) 0.001 & *** \\
        \hdashline
        \multirow{5}{*}{Interactions}
         & sl : Water & -0.305 & 0.076 & \(<\) 0.001 & *** \\
         & sl : Woodland & -0.089 & 0.039 & 0.023 & ** \\
         & sl : Shrubs/Grassland & 0.124 & 0.058 & 0.032 & ** \\
         & sl : DistanceToWater \textsuperscript{0.5} & -0.058 & 0.031 & 0.056 & * \\
         & cos(ta) : HumanInfluence & -0.040 & 0.022 & 0.070 & * \\
         & cos(ta) : DistanceToWater \textsuperscript{0.5} & 0.063 & 0.026 & 0.017 & ** \\
         \bottomrule
      \end{tabular}
       \begin{tablenotes}
         \item \textit{Significance codes: * \(p < 0.10\) \quad ** \(p < 0.05\)
         \quad *** \(p < 0.01\)}
       \end{tablenotes}
    \end{threeparttable}
    }
  \end{center}
\end{table}

### 2021-09-08 Chapter_1/04_Manuscript/Manuscript_Support.tex
Various updates

\documentclass[abstract=off,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
% \usepackage{lineno}
\usepackage{multirow}
\usepackage{arydshln}
% \usepackage[nomarkers, nolists]{endfloat}
\usepackage[flushleft]{threeparttable}

@@

\textbf{Keywords:} dispersal, habitat selection, integrated step selection
function, Kavango-Zambezi Transfrontier Conservation Area, landscape
connectivity, least-cost corridors, Lycaon pictus, permeability surface,
protected areas, wildlife management

@@

%------------------------------------------------------------------------------
%	Appendix S1: All Movement Models
%------------------------------------------------------------------------------
\section{Movement Models}
% latex table generated in R 3.6.3 by xtable 1.8-4 package
% Thu Jul  9 09:17:26 2020
\begin{table}[hbpt]
  \caption{Results from the forward model selection procedure based on Akaike's
  Information Criterion (AIC; \citealp{Burnham.2002}) for the movement model.
  The base model upon which we based our movement model is depicted in the last
  row. We omitted all models with an AIC weight of zero.}
  \label{ModelAICs}
  \begin{center}
    \resizebox{\textwidth}{!}{
      \begin{threeparttable}
        \begin{tabular}{lllll}
        \toprule
          Covariates & AIC & \(\Delta\)AIC & Weight & LogLik \\
          \midrule
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) & 89392.88 & 0.00 & 0.15 & -44670.44 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + SH:log(sl) & 89393.92 & 1.04 & 0.09 & -44669.96 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + DTW:log(sl) & 89394.13 & 1.25 & 0.08 & -44670.06 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WO:log(sl) & 89394.25 & 1.37 & 0.08 & -44670.13 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl & 89394.36 & 1.48 & 0.07 & -44672.18 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + log(sl):LA & 89394.44 & 1.56 & 0.07 & -44670.22 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + HI:sl & 89394.56 & 1.68 & 0.07 & -44670.28 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WA:log(sl) & 89394.57 & 1.69 & 0.07 & -44670.29 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WO:cos(ta) & 89394.59 & 1.71 & 0.07 & -44670.30 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WA:cos(ta) & 89394.63 & 1.75 & 0.06 & -44670.31 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + sl:cos(ta) & 89394.68 & 1.80 & 0.06 & -44672.34 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + HI:log(sl) & 89394.69 & 1.81 & 0.06 & -44670.35 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + SH:cos(ta) & 89394.84 & 1.96 & 0.06 & -44670.42 \\
          \hdashline
          \\
          \vdots & \vdots & \vdots & \vdots & \vdots \\
          \\
          \hdashline
          \\
          \textbf{Base Model}: cos(ta) + sl + log(sl) + WA + WO + DTW + HI + SH & 90091.40 & 787.67 & 0.00 & -45030.70\\
          \\
         \bottomrule
       \end{tabular}
       \begin{tablenotes}
         \item \textit{Note:} ta = Turning Angle, sl = Step Length, LA = Low Activity, WA = Water,
         DTW = Distance To Water, SH = Shrubs/Grassland, WO = Woodland, HI =
         Human Influence.
       \end{tablenotes}
     \end{threeparttable}
    }
  \end{center}
\end{table}

% \begin{figure}[htpb]
%   \begin{center}
%     \includegraphics[width = \textwidth]{99_MovementModelAICs.png}
%     \caption{Coefficients of all movement models with an AIC weight above zero.}
%     \label{AllMovementModels}
%   \end{center}
% \end{figure}

%------------------------------------------------------------------------------
%	Appendix S2: Evolution of Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Evolution of Heatmaps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.88\textwidth]{99_HeatmapsIndividual.png}
    \caption{Heatmaps produced after 125, 500, and 2000 simulated steps,
    respectively. The left panel (a1, a2, a3) was generated based on simulations
    initiated within the main study area, the right panel (b1, b2, b3) was
    generated based on simulations initiated within the buffer area. To produce
    the heatmap presented in the main text, we summed up values from maps a3 and
    b3.}
    \label{Trajectories}
  \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S3: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Evolution of Betweenness}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.88\textwidth]{99_BetweennessIndividual.png}
    \caption{Maps of betweenness scores produced after 125 (a), 500 (b), and
    2000 (c) simulated steps, respectively. A high betweenness score indicates
    that the respective area is paramount for linking other regions in the study
    area. It therefore highlights movement corridors that provide access to
    various destinations.}
    \label{Trajectories}
  \end{center}
\end{figure}
\restoregeometry

>>>>

\documentclass[abstract=off,10pt,a4paper,bibliography=totocnumbered]{article}
\usepackage[paper=a4paper,left=35mm,right=35mm,top=25mm,bottom=30mm]{geometry}
\usepackage[doublespacing]{setspace}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{colortbl}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink]{cleveref}
% \usepackage{lineno}
\usepackage{multirow}
\usepackage{arydshln}
% \usepackage[nomarkers, nolists]{endfloat}
\usepackage[flushleft]{threeparttable}
\usepackage{pdflscape}

@@

\textbf{Keywords:} dispersal, simulation, movement, integrated step selection
function, Kavango-Zambezi Transfrontier Conservation Area, landscape
connectivity, Lycaon pictus

@@

%------------------------------------------------------------------------------
%	Appendix S1: Source Points
%------------------------------------------------------------------------------
\newpage
\section{Source Areas \& Points}
\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width = \textwidth]{99_SourceAreas.png}
    \caption{(a) Different source areas from which we released virtual
    dispersers. We only considered contiguous protected areas (national parks,
    game reserves, and forest reserves) that were larger than 700
    km\textsuperscript{2}. This size corresponds to the average home range
    requirement for viable wild dog populations \citep{Pomilia.2015}. To render
    potential immigrants into the study system, we also initiated dispersers
    within a buffer zone (blue) surrounding the main study area. (b) Source
    points from which dipsersers were released. 50'000 dispersers were released
    within the main study area (green dots) and another 30'000 dispersers within
    the virtual buffer (blue dots).}
    \label{SourcePoints}
  \end{center}
\end{figure}

%------------------------------------------------------------------------------
%	Appendix S2: All Movement Models
%------------------------------------------------------------------------------
\newpage
\begin{landscape}
\thispagestyle{empty}
\section{Model Selection Results}
% latex table generated in R 3.6.3 by xtable 1.8-4 package
% Thu Jul  9 09:17:26 2020
\begin{table}[hbpt]
  \caption{Results from the forward model selection procedure based on Akaike's
  Information Criterion (AIC; \citealp{Burnham.2002}). The model in the top row
  was the model that we used to simulate movement of dispersers. The base model
  upon which we based our movement model is depicted in the last row. We omitted
  all models with an AIC weight of zero from the table.}
  \label{ModelAICs}
  \begin{center}
    \resizebox{1.75\textwidth}{!}{
      \begin{threeparttable}
        \begin{tabular}{lllll}
        \toprule
          Covariates & AIC & \(\Delta\)AIC & Weight & LogLik \\
          \midrule
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) & 89392.88 & 0.00 & 0.15 & -44670.44 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + SH:log(sl) & 89393.92 & 1.04 & 0.09 & -44669.96 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + DTW:log(sl) & 89394.13 & 1.25 & 0.08 & -44670.06 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WO:log(sl) & 89394.25 & 1.37 & 0.08 & -44670.13 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl & 89394.36 & 1.48 & 0.07 & -44672.18 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + log(sl):LA & 89394.44 & 1.56 & 0.07 & -44670.22 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + HI:sl & 89394.56 & 1.68 & 0.07 & -44670.28 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WA:log(sl) & 89394.57 & 1.69 & 0.07 & -44670.29 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WO:cos(ta) & 89394.59 & 1.71 & 0.07 & -44670.30 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + WA:cos(ta) & 89394.63 & 1.75 & 0.06 & -44670.31 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + sl:cos(ta) & 89394.68 & 1.80 & 0.06 & -44672.34 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + HI:log(sl) & 89394.69 & 1.81 & 0.06 & -44670.35 \\
          \textbf{Base Model} + sl:LA + WA:sl + log(sl):cos(ta) + DTW:cos(ta) + WO:sl + HI:cos(ta) + SH:sl + DTW:sl + sl:cos(ta) + SH:cos(ta) & 89394.84 & 1.96 & 0.06 & -44670.42 \\
          \hdashline
          \\
          \vdots & \vdots & \vdots & \vdots & \vdots \\
          \\
          \hdashline
          \\
          \textbf{Base Model}: cos(ta) + sl + log(sl) + WA + WO + DTW + HI + SH & 90091.40 & 787.67 & 0.00 & -45030.70\\
          \\
         \bottomrule
       \end{tabular}
       \begin{tablenotes}
         \item \textit{Note:} ta = Turning Angle, sl = Step Length, LA = Low Activity, WA = Water,
         DTW = Distance To Water, SH = Shrubs/Grassland, WO = Woodland, HI =
         Human Influence.
       \end{tablenotes}
     \end{threeparttable}
    }
  \end{center}
\end{table}
\vfill
\raisebox{-1cm}{\makebox[\linewidth]{\thepage}}
\end{landscape}

%------------------------------------------------------------------------------
%	Appendix S3: Movement Model interpretation
%------------------------------------------------------------------------------
\newpage
% \newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Movement Model Interpretation}
To ease with the interpretation of the most parsimonious movement model, we
followed recommendations published in \cite{Fieberg.2020} and produced a series
of plots highlighting how the habitat and movement kernel depended on covariate
values (\Cref{Interpretation}). To visualize the movement kernel and its
interactions with other covariates, we used model estimates and updated our
tentative distribution parameters for turning angles (von Mises distribution
with concentration \(\kappa = 0\)) and step lengths (gamma distribution with
scale \(\theta\) = 6'308 and shape \(k\) = 0.37) by applying the function
\textsf{update\_vonmises()} from the R-package \textsf{amt} \citep{Amt.2019}.
This allowed us to compute probability densities of turning angles and step
lengths under varying values of the associated covariates, while holding all
other covariates constant (\Cref{Interpretation}, a1-a8). Moreover, we
investigated the habitat kernel by computing relative selection strengths (RSS)
between a set of steps where values of the covariate of interest was varied to a
reference step where the covariate value was fixed to its centered value. To
illustrate model uncertainty, we also generated large-sample confidence
intervals using standard errors associated with each model estimate
(\Cref{Interpretation}, b1-b5).

\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = \textwidth]{99_MovementModelInterpretation.png}
    \caption{Auxiliary plots that help with the interpretation of the most
    parsimonious movement model from Table S1. The plots were generated
    following recommendations reported in \cite{Fieberg.2020}. Subplots
    \textbf{a1} to \textbf{a8} highlight dispersing wild dogs' movement kernel
    and indicate how the kernel is influenced by interactions with other
    covariates. Subplots \textbf{b1} to \textbf{b5} depict results from
    dispersing wild dogs' habitat kernel and highlight differences in predicted
    relative selection scores (RSS) when varying values of the covariate of
    interest. For each covariate, predictions were made on the range of values
    that was observed in the real data, assuming that all other covariates were
    centered and that steps were realized during periods of ``high'' wild dog
    activity. Plot a1, for example, can be interpreted as follows: the
    probability of realizing a step with a low turning angle is much higher when
    the corresponding step is large. Moreover, b1 can be interpreted as follows:
    relative probability of using a step decreases as the amount of water cover
    along the step increases.}
    \label{Interpretation}
  \end{center}
\end{figure}
% \restoregeometry

%------------------------------------------------------------------------------
%	Appendix S4: Heatmaps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=5mm,footskip=0pt}
\section{Heatmaps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_HeatmapsIndividual.png}
    \caption{Heatmaps produced when considering 125, 500, and 2000 simulated
    steps, respectively. The left panel (a1, a2, a3) was generated based on
    simulations initiated within the main study area, the right panel (b1, b2,
    b3) was generated based on simulations initiated within the buffer area. To
    produce the heatmap presented in the main manuscript (Figure 5), we tallied
    the values from maps a3 and b3.}
    \label{Heatman}
  \end{center}
\end{figure}
\restoregeometry

%------------------------------------------------------------------------------
%	Appendix S5: Evolution of Betweenness Maps
%------------------------------------------------------------------------------
\newpage
\newgeometry{left=35mm,right=35mm,top=25mm,bottom=10mm,footskip=0pt}
\section{Betweenness Maps in Relation to Number of Simulated Steps}
\begin{figure}[hbtp]
  \begin{center}
    \includegraphics[width = 0.86\textwidth]{99_BetweennessIndividual.png}
    \caption{Maps of betweenness scores produced when considering (a) 125, (b)
    500, (c) and 2000 simulated steps, respectively. A high betweenness score
    indicates that the respective area has a high importance for linking other
    regions in the study area.}
    \label{Betweenness}
  \end{center}
\end{figure}
\restoregeometry
